{\sf NodIO}, a framework for evolutionary algorithms in JavaScript: first results

### 2016-01-06 special-issue-ci/volunteer-clouds-ieee-ci-si-tr.tex
Few changes

JavaScript is an interpreted language mainly known for its inclusion
as an embedded language for programming internet browsers. This has
inspired its use, for a long time, as a tool for evolutionary
algorithms, mainly so in browser-based volunteer computing
environments. Several libraries have also been published so far and are in
use. However, the last years have seen a resurgence of interest in the
language, becoming one of the most popular and thus spawning the
improvement of its implementations, which form now the base of many
new client-server applications. We present such an application for
running distributed or volunteer-based evolutionary algorithm
experiments, and we make a series of
measurements to establish the speed of JavaScript in evolutionary
algorithms that can serve as a baseline for comparison with other
distributed computing experiments. These experiments use different
integer and floating point problems, and prove that the speed of
JavaScript is actually competitive with other languages commonly used
by the evolutionary algorithm practitioner.

@@

The need to use non-permanent and potentially massive computing
infrastructure for distributed scientific experiments has lead to the
rising of {\em volunteer computing} as a set of tools that allow
citizens to {\em donate} cycles to scientific experiments by running
an application \cite{Anderson06thecomputational}; this application can be embedded in a web page. And
since browsers are ubiquitous, these kind of systems are the ones that
interest we the most and has led us to create a framework for
evolutionary algorithm experiments that is able to work in that mode
\cite{DBLP:journals/corr/GuervosG15}. {\sf NodIO} is a
cloud or bare metal based volunteer evolutionary computing system
derived from the {\sf NodEO} library, whose architecture has been
developed using JavaScript on the client as well as the server.
All parts of the framework are free and available with a free license
from \url{https://github.com/JJ/splash-volunteer}.

>>>>

JavaScript is an interpreted language mainly known for its inclusion
as an embedded language for programming web browsers. This has
inspired its use, for a long time, as a tool for evolutionary
algorithms, mainly so in browser-based volunteer computing
environments. Several libraries have also been published so far and are in
use. However, the last years have seen a resurgence of interest in the
language, becoming one of the most popular and thus spawning the
improvement of its implementations, which are now the foundation of many
new client-server applications. We present such an application for
running distributed volunteer-based evolutionary algorithm 
experiments, and we make a series of
measurements to establish the speed of JavaScript in evolutionary
algorithms that can serve as a baseline for comparison with other
distributed computing experiments. These experiments use different
integer and floating point problems, and prove that the speed of
JavaScript is actually competitive with other languages commonly used
by the evolutionary algorithm practitioner.

@@

The need to use non-permanent and potentially massive computing
infrastructure for distributed scientific experiments has lead to the
rising of {\em volunteer computing} defined as a set of tools that allow
citizens to {\em donate} cycles to scientific experiments by running
an application \cite{Anderson06thecomputational}; this application can be embedded in a web page. And
since browsers are ubiquitous, these kind of systems are the ones that
we are interested the most and this has led us to create a framework for
evolutionary algorithm experiments that is able to work in that mode
\cite{DBLP:journals/corr/GuervosG15}. {\sf NodIO} is a
cloud or bare metal based volunteer evolutionary computing system
derived from the {\sf NodEO} library, whose architecture has been
developed using JavaScript on the client as well as the server.
All parts of the framework are free and available with a free license
from \url{https://github.com/JJ/splash-volunteer}.
